The title

### 2017-11-02 article.tex
Plenty

\section{Overview}
Looking for possibilities (weak acceptance). Those propositions that are in the reflexive preferences in a large sense: there is no strong enough reason to reject those propositions, though their contrary may hold as well.
\begin{itemize}
	\item All alternatives $\allalts$.
	\item Topic $\alltopic$ = $\Set{\prop_\alt, \alt \in \allalts} ∪ \Set{\prop_{¬\alt}, \alt \in \allalts}$. Denoted simply $\alt$ and $¬\alt$. We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
	\item All possible arguments: $\allargs$, the set of all strings. It can be chosen differently, but must be non empty as it contains at least $\emptyset$, the empty argument.
	\item $\ar' \nibeatsst[\prop] \ar$: absence, all the time, of strong rejection attack; $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it. This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$ (it is clear we can’t observe it, thus, as we can’t observe the DP). With $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar'$ supports that $\prop$ is not weakly accepted, thus $\ar$, if rebutted, can’t be used even to say that $\prop$ is a possibility. Thus we have only attacks between contradictory propositions. Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments) to negate $\ar' \nibeatsst[\prop] \ar$. Here we do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement. Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\ar$ at all; or is not understood by $i$. Note that when $\ar' \nibeatsst[\prop] \ar$, further attacks to $\ar'$ have no chance to change that fact (assuming some properties over the way $i$ reason). The negation of this should read: $\ar'$ may attack $\ar$ in at least some cases. For example, $¬ (\ar' \nibeatsst[\prop] \ar)$ ($\ar'$ may attack $\ar$) in case $i$ suspects that $\ar'$ is invalid (because of some counter-argument $\ar_2$ to $\ar'$ that $i$ has in mind) but wants to leave the door open to reinstatement of $\ar'$.
	\item Define $¬ (\ar' \nibeatsst[\prop] \ar)$ iff $\ar' \ibeatse[\prop] \ar$.
	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure). Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$. Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $¬(\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar' \ibeatsst[\prop] \ar ⇒ \ar' \ibeatse[\prop] \ar$.
\end{itemize}
It seems that knowledge of the poss rels is insufficient to know the sure rel: assume $¬(\ar' \ibeatse[\prop] \ar)$ and $\ar \ibeatse[¬\prop] \ar'$. Thus, 1. $\ar$ is sufficient for $\prop$ possible, $\ar'$ not sufficient for $¬\prop$ sure; and 2. $\ar$ may be sufficient for $\prop$ sure, $\ar'$ insuff for $\prop$. But is $\ar$ sufficient for $\prop$ sure? Thus, $\ar' \ibeatse[\prop, \text{sure}] \ar$? Equivalently: $\ar \nibeatse[¬\prop] \ar'$? To know this we need to know whether $¬\prop \in T_i$. Or can we use $¬(\ar' \ibeatse[\prop] \ar) ⇒ \ar' \nibeatse[\prop] \ar$?

Previously:
\begin{itemize}
	\item $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
	\item Require (as an axiom) that $\ar' \ibeatse[\prop] \ar ∨ \ar' \nibeatse[\prop] \ar$. This yields $¬ (\ar' \ibeatsst[\prop] \ar ∧ \ar' \nibeatsst[\prop] \ar)$.
\end{itemize}

Define $T_i \subseteq \alltopic$ as the set of propositions that are weakly accepted.
\begin{definition}[Weak acceptance]
	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$. A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in T_i$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
\end{definition}
It follows that $¬\prop \notin T_i$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$.

\begin{definition}[Strong rejection]
	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$. A proposition $¬\prop \in \alltopic$ is strongly rejected iff $\forall \ar \in \allargs, \exists \ar' \in \allargs \suchthat \ar \nibeatsst[\prop, \text{sure}] \ar'$.
\end{definition}
Thus, strong rejection mandates $\ar'$ such that $\ar' \ibeatsst[¬\prop] \ar$.

If $¬\prop$ is strongly rejected, then it is not weakly accepted ($¬\prop \notin T_i$) as $\ar' \ibeatsst[¬\prop] \ar ⇒ \ar' \ibeatse[¬\prop] \ar$.

\begin{definition}[Clear-cut]
	A situation is clear-cut iff $¬\prop \notin T_i ⇒ ¬\prop$ is strongly rejected.
\end{definition}

First, we want that if situation is CC, 1) exists a valid model, 2) any valid model has the right $T_i$.
A model is valid if: a) can correctly get reinstatement; b) i is justifiably unstable; c) finite arguments; d) model is convincing.

Second, we want that given a situation, if there exists a valid model, then the situation is CC.

Third, perhaps we get as a bonus that there exists a valid model ⇔ the situation is CC3. CC1: ¬p not in wa ⇔ ¬p s rej. CC2: ¬p s rej ⇒ p w acc. CC3: ¬p s rej ⇒ p is sure.

\section{Models}
$\mbeats$ a (possibly infinite!) DAG over $(s, p)$ pairs, $+$ defined over arguments in $\mbeats$: $(\ar_1, \prop) + (\ar_3, \prop) = (\ar', \prop)$ for some $(\ar', \prop) \in \mbeats$. Define $D' \subseteq \clargs$ as a subset of arguments (those supporting propositions). Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats$. Assume it can be represented by $≥$, a weak order defined on the basis of $\mbeats$, defining at most $k$ equivalence classes, so that our recursive definitions make sense. (TODO make this correct and precise.)

$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$.

Given $\ar_1 \in D'$, define $\ar_2 \wibeatse \ar_1$ iff $\ar_2 \ibeatse \ar_1$.

Given $\ar_1 \in D'$, define $\ar_2 \nwibeatse \ar_1$ iff $\ar_1 \ibeatse[\text{sure}] \ar_2$.

Define $\ar_1 \wibeatse[\text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse \ar_1$.

$\ar_1$ root in $\mbeats$ $⇒$ $\ar_1 \in D'$. $\ar_1 \in D' ⇒ \ar_3 + \ar_1 \in D'$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \nwibeatse \ar_3 + \ar_1$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \nwibeatse \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1 ∧ \ar_2 \wibeatse \ar_3 + \ar_1$.

Check: For $\ar_4, \ar_3, \ar_3 \notin D'$: $\ar_4 \wibeatse \ar_3$ iff $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \ar_3 \nwibeatse \ar_4 + \ar_2$. Thus, $\exists \ar_2 \suchthat  \ar_3 \wibeatse \ar_2 ∧ \exists \ar_1 \suchthat (\ar_4 + \ar_2) \wibeatse \ar_1 ∧ (\ar_4 + \ar_2) \wibeatse \ar_3 + \ar_1$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse \ar_1$, we have: $\ar_3 \wibeatse \ar_2 ∨ \ar_3 \nwibeatse \ar_2$.

Define $\wibeatsst = ¬\nwibeatse$. Hence, $¬(\ar \wibeatse[\text{sure}] \ar') ⇔ \ar \nwibeatsst[\text{sure}] \ar' ⇔ ¬(\ar' \nwibeatse \ar) ⇔ \ar' \wibeatsst \ar$.

Define $\nwibeatsst = ¬\wibeatse$.

Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin D'$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.

\section{Conditions}
\begin{definition}[Reinstatement]
	Given a model $\mu = (\mbeats, D')$ and a decision situation $(\allalts, \allargs, \ibeatse)$, given $\ar_1 \in D', \ar_2 \mbeats \ar_1, \ar_2 \wibeatse \ar_1, \ar_3 \wibeatse \ar_2, \mbeatsinv(\ar_3) = \emptyset$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_1 + \ar_3) ∧ \mbeatsinv(\ar_1 + \ar_3) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
\end{definition}

\begin{definition}[Observable validity]
	Given as above, the model is observably valid iff $\forall \ar_2 \mbeats \ar: ¬(\ar_2 \wibeatse \ar) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
\end{definition}

\begin{definition}[Justifiable unstability]
	Given as above…
\end{definition}

>>>>

\section{Overview}
Looking for possibilities (weak acceptance). Those propositions that are in the reflexive preferences in a large sense: there is no strong enough reason to reject those propositions, though their contrary may hold as well.
\begin{itemize}
	\item All alternatives $\allalts$.
	\item Topic $\alltopic$ = $\Set{\prop_\alt, \alt \in \allalts} ∪ \Set{\prop_{¬\alt}, \alt \in \allalts}$. Denoted simply $\alt$ and $¬\alt$. We define $¬\prop$, with $\prop = \prop_\alt$, as equal to $\prop_{¬\alt}$ and $¬\prop$, with $\prop = \prop_{¬\alt}$, as equal to $\prop_{\alt}$.
	\item All possible arguments: $\allargs$, the set of all strings. It can be chosen differently, but must be non empty as it contains at least $\emptyset$, the empty argument.
	\item $\ar' \nibeatsst[\prop] \ar$: absence, all the time, of strong rejection attack; $\ar'$ does not render $\ar$ invalid; it is sure that $\ar'$ has no impact on $\ar$, even assuming that $\ar'$ would in turn resist all counter-arguments to it. This is an hypothesized relation, unobservable, used to define the deliberated preferences of $i$ (it is clear we can’t observe it, thus, as we can’t observe the DP). With $\ar$ supporting $\prop$, $\ar'$ claims that $¬\prop$ is a certainty, thus $\ar'$ supports that $\prop$ is not weakly accepted, thus $\ar$, if rebutted, can’t be used even to say that $\prop$ is a possibility. Thus we have only attacks between contradictory propositions. Suffices that the attack occurs at least once over the considered time frame and unstability factors (such as submitting $i$ to other counter-arguments) to negate $\ar' \nibeatsst[\prop] \ar$. Here we do not condition on $\ar'$ surviving: $\ar'$ is declared incorrect, with no necessity of pursuing the debate and no hope of reinstatement. Example: $\ar'$ has already been taken into account and countered in $\ar$; or $\ar'$ does not talk about $\ar$ at all; or is not understood by $i$. Note that when $\ar' \nibeatsst[\prop] \ar$, further attacks to $\ar'$ have no chance to change that fact (assuming some properties over the way $i$ reason). The negation of this should read: $\ar'$ may attack $\ar$ in at least some cases. For example, $¬ (\ar' \nibeatsst[\prop] \ar)$ ($\ar'$ may attack $\ar$) in case $i$ suspects that $\ar'$ is invalid (because of some counter-argument $\ar_2$ to $\ar'$ that $i$ has in mind) but wants to leave the door open to reinstatement of $\ar'$.
	\item Define $¬ (\ar' \nibeatsst[\prop] \ar)$ iff $\ar' \ibeatse[\prop] \ar$.
	\item Define $\args^\prop$ as the decisive arguments in favor of $\prop$: $\ar \in \args^\prop ⇔ \nexists \ar' \ibeatse[\prop] \ar ⇔ \ar' \nibeatsst[\prop] \ar$.
	\item Define $\ar \ibeatse[¬\prop, \text{sure}] \ar'$ iff $\ar$ may attack $\ar'$, where $\ar$ has a weak claim ($\prop$ is possible) and $\ar'$ has a strong claim ($¬\prop$ is sure). Similarly, $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ is a constant absence of attack.
	\item Define $\args^{¬\prop, \text{sure}}$ as the decisive arguments in favor of $¬\prop, \text{sure}$: $\ar' \in \args^{¬\prop, \text{sure}} ⇔ \nexists \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.
	\item Require (axiom A1) that $\ar' \ibeatse[\prop] \ar ∨ \ar \ibeatse[¬\prop, \text{sure}] \ar'$. Equivalently: $¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar' ∧ \ar' \nibeatsst[\prop] \ar)$; $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar' \ibeatse[\prop] \ar$.
	\item Axiom A2: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇒ \ar \nibeatsst[¬\prop] \ar'$. Equivalently: $\ar \ibeatse[¬\prop] \ar' ⇒ \ar \ibeatse[¬\prop, \text{sure}] \ar'$.
	\footnote{A3: $[\exists \ar \suchthat (\ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar')] ⇒ \exists \ar_2 \suchthat \ar_2 \ibeatse[¬\prop] \ar'$. Equivalently: $\ar_2 \nibeatsst[¬\prop] \ar', \forall \ar_2$ implies that for all $\ar$, $(\ar' \nibeatsst[\prop] \ar ∨ \ar \nibeatsst[¬\prop, \text{sure}] \ar')$. A1, A2 and A3 are equivalent to: $\ar \nibeatsst[¬\prop, \text{sure}] \ar' ⇔ \ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar$.}
	\footnote{Having A1 and A2, can we have $\ar \nibeatsst[¬\prop] \ar' ∧ \ar' \ibeatse[\prop] \ar ∧ \ar \ibeatse[¬\prop, \text{sure}] \ar'$? Consider $(\ar', ¬\prop) \succeq (\ar, \prop) \sim (\ar', ¬\prop, \text{sure}) \succeq (\ar, \prop, \text{sure})$.}
\end{itemize}

It seems that knowledge of the poss rels is insufficient to know the sure rel: assume $¬(\ar' \ibeatse[\prop] \ar)$ and $\ar \ibeatse[¬\prop] \ar'$. Thus, 1. $\ar$ is sufficient for $\prop$ possible, $\ar'$ not sufficient for $¬\prop$ sure; and 2. $\ar$ may be sufficient for $\prop$ sure, $\ar'$ insuff for $\prop$. But is $\ar$ sufficient for $\prop$ sure? Thus, $\ar' \ibeatse[\prop, \text{sure}] \ar$? Equivalently: $\ar \nibeatse[¬\prop] \ar'$? To know this we need to know whether $¬\prop \in \iposs$. Or can we use $¬(\ar' \ibeatse[\prop] \ar) ⇒ \ar' \nibeatse[\prop] \ar$?

Previously:
\begin{itemize}
	\item $¬ (\ar' \ibeatsst[\prop] \ar) ⇔ \ar' \nibeatse[\prop] \ar ⇔ \ar \ibeatse[¬\prop, \text{sure}] \ar' ⇔ ¬ (\ar \nibeatsst[¬\prop, \text{sure}] \ar')$.
\end{itemize}

Define $\iposs \subseteq \alltopic$ as the set of propositions that are weakly accepted.
\begin{definition}[Weak acceptance]
	Define a situation $(\allalts, \allargs, \set{\ibeatse[\prop]})$. A proposition $\prop \in \alltopic$ is weakly accepted, $\prop \in \iposs$, iff $\exists \ar \in \allargs \suchthat \forall \ar' \in \allargs: \ar' \nibeatsst[\prop] \ar$.
\end{definition}
It follows that $¬\prop \notin \iposs$ iff $\forall \ar: \exists \ar' \suchthat \ar' \ibeatse[¬\prop] \ar$. Equivalently, $¬\prop \notin \iposs ⇔ \ibeatse[¬\prop](\allargs) = \allargs$.

\begin{definition}[Sure acceptance]
	$¬\prop \in \isure$ iff $\exists \ar' \in \allargs \suchthat \forall \ar \in \allargs: \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.\footnote{Instead of accepting $¬\prop$ for sure, it is tempting to define strong rejection of $t$ as follows. A proposition $\prop \in \alltopic$ is strongly rejected iff $\forall \ar_0 \in \allargs, \exists \ar' \in \allargs \suchthat \ar_0 \nibeatsst[¬\prop, \text{sure}] \ar'$. But this is too weak: we want $\ar'$ to be also decisive, thus $\ar \nibeatsst[¬\prop, \text{sure}] \ar', \forall \ar$. Hence the definition becomes $\exists \ar' \in \allargs \suchthat \ar \nibeatsst[¬\prop, \text{sure}] \ar'$.}
\end{definition}
If $¬\prop \in \isure$, then $\prop \notin \iposs$: with $\ar' \in \args^{¬\prop, \text{sure}}$, given any $\ar$, $\ar' \ibeatse[\prop] \ar$ (because $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$, see A1).

If $¬\prop \in \isure$, then $¬\prop \in \iposs$: from $\ar \nibeatsst[¬\prop, \text{sure}] \ar'$ we obtain $\ar \nibeatsst[¬\prop] \ar'$ using A2.

\begin{definition}[Clear-cut]
	A situation is clear-cut iff $\prop \notin \iposs ⇒ ¬\prop \in \isure$.
\end{definition}
Here is an example of a non clear-cut situation. $\allargs = \{\emptyset\}, \alltopic = \{\prop\}, \emptyset \ibeatse[\prop] \emptyset, \emptyset \ibeatse[¬\prop, \text{sure}] \emptyset$.

\section{Models}
$\mbeats$ an acyclic binary relation over $\allargs$ (by which we mean that its transitive closure is irreflexive). $\mleadsto \subseteq \allargs × \alltopic$. Define $\clargs \subseteq \allargs$ as the set of arguments used in $\mbeats ∪ \mleadsto$. Let $+$ be defined over arguments used in the model: $\ar_3 + \ar_1 = \ar'$ for some $\ar' \in \clargs$, for any $\ar_3, \ar_1 \in \clargs$.

Requirements. The maximum length of a path in $\mbeats$ is finite.
$\ar_3 \mbeats \ar_2 \mbeats \ar_1 ⇒ \ar_2 \mbeats \ar_3 + \ar_1$.\footnote{Necessary for definition of $\ar_3 \wibeatse \ar_2$.}

Notation. Let $\mleadstoinv(\alltopic) \subseteq \clargs$ denote the subset of arguments supporting propositions. 
$\mbeats(\ar_2)$: arguments that $\ar_2$ attacks, $\ar_1 \in \mbeats(\ar_2) ⇔ \ar_2 \mbeats \ar_1$. We write $\args \mbeats \ar$ to mean that $\forall \ar' \in \args: \ar' \mbeats \ar$, and similarly for other binary relations.

Given a decision situation, define $\wibeatse \subseteq \mbeats$ as follows.

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \ileadsto \prop ∧ \ar_3 \ibeatse[\prop] \ar_2]$.

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ \ar_2 \ibeatse[¬\prop, \text{sure}] \ar_3]$.
\footnote{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
\begin{itemize}
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\prop] \ar_2) ∧ (\ar_3 \nwibeatse[\prop] \ar_4 + \ar_2)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_3 + \ar_1 \ibeatse[¬\prop, \text{sure}] \ar_2) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_1 ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ \ar_4 + \ar_2 \ibeatse[\prop] \ar_3 + \ar_1)]$.
\end{itemize}
}

TODO this is well-defined because associate to each $\ar \in \clargs$ $d(\ar)$, the distance to the farthest root (a root is an argument that $\mbeats$-attacks nobody). Then $\wibeatse$ is defined for all attacks from $d(.)=1$ nodes (because those nodes attack only $d(.)=0$ nodes), and thus is defined for all nodes $2$, I suppose, …

Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1$, we have: $\ar_3 \wibeatse[\prop] \ar_2 ∨ \ar_3 \nwibeatse[\prop] \ar_2$.

Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \prop \in \alltopic \suchthat \ar_2 \wibeatse[\prop] \ar_1$.

Define $\wibeatsst = ¬\nwibeatse$. Define $\nwibeatsst = ¬\wibeatse$.

Hence, given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic)$: $\ar_3 \wibeatsst \ar_2$ iff $\forall \ar_1 \in \mbeats(\ar_2) ∩ \wibeatse(\ar_2): \ar_2 \nwibeatsst \ar_3 + \ar_1$.

\subsection{Certainties}
Assume we define $\ar_1 \wibeatse[¬\prop, \text{sure}] \ar_2$ ⇔ $\ar_2 \nwibeatse[\prop] \ar_1$. Then, indeed, given $\ar_1 \mleadsto \prop$, $\ar_2 \wibeatse[¬\prop, \text{sure}] \ar_1$ ⇔ $\ar_2 \ibeatse[¬\prop, \text{sure}] \ar_1$. But it gives the wrong conclusion. For $\ar_3 \mbeats \ar_2 \mbeats \ar_1 \mleadsto t: \ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\ar_2 \nwibeatse[¬\prop] \ar_3$ iff $\exists \ar_1 \in \mbeats(\ar_3) \suchthat \ar_3 \wibeatse[¬\prop] \ar_1 ∧ \ar_3 \wibeatse[¬\prop] \ar_2 + \ar_1$.

Given $\ar_1 \mleadsto \prop$, define $\ar_2 \wibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_2 \ibeatse[\prop, \text{sure}] \ar_1$.

Given $\ar_1 \mleadsto \prop$, define $\ar_2 \nwibeatse[\prop, \text{sure}] \ar_1$ iff $\ar_1 \ibeatse[¬\prop] \ar_2$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \wibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \nwibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.

Given $\ar_3 \in \clargs, \ar_2 \in \clargs, \ar_2 \notin \mleadstoinv(\alltopic), \prop \in T$: $\ar_3 \nwibeatse[\prop, \text{sure}] \ar_2$ iff $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop, \text{sure}] \ar_1 ∧ \ar_2 \wibeatse[\prop, \text{sure}] \ar_3 + \ar_1$.

\section{Conditions}
All these conditions assume that a decision situation $(\allalts, \allargs, \{\ibeatse[\prop]\})$ and a model $\eta = (\mbeats, \mleadsto, +)$ are given.

Define $\argsdec = \clargs \setminus \text{im}(\wibeatse)$ the decisive arguments according to $\wibeatse$, or $\wibeatse$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv(\ar) = \emptyset$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3 \in \argsdec$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse \ar_1, \ar_2 \nwibeatse \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse \ar_2$.
\end{definition}

\begin{definition}[Finite defense]
	If $\wibeatseinv(\ar) \subseteq \wibeatse(\argsdec)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse(\args)$.
\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec as: $\wibeatseinv(\ar) \subseteq \wibeatse(\clargs \setminus \text{im}(\mbeats)) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args)$. Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is insufficient to provide $T_\eta = \iposs$. Define $\ar' \mbeats^\text{fail} \ar$ iff $\ar' \mbeats \ar ∧ ¬(\ar' \wibeatse \ar)$. Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_4 \mbeats^\text{fail} \{\ar_3, \ar_3', …\}$. Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\wibeatse$-$\wibeatse$-$\mbeats$-dec is artificially satisfied because the antecedent fails to trigger.}
\footnote{Define Finite defense-$\wibeatse$-$\wibeatse$-subsets as: $\wibeatseinv(\ar) \subseteq \wibeatse(\args) ⇒ \wibeatseinv(\ar) \subseteq \wibeatse(\args')$. Finite defense-$\wibeatse$-$\wibeatse$-subsets is insufficient to provide $T_\eta = \iposs$. This is because Reinstatement allows for new attacks in $\wibeatse$ (it only forbids new attacks in $\mbeats$), thus we can forever transform previously failing attacks to new attacks, hence always satisfying Finite defense (always finite cover of $\wibeatse$, but infinite cover of $\mbeats$) but still not converging. Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \mbeats^\text{fail} \ar_1$, and so on; and $\ar_3' \wibeatse \ar_2' \wibeatse \ar_3 + \ar_1, \ar_3'' \wibeatse \ar_2'' \mbeats^\text{fail} \ar_3 + \ar_1$, and so on.}
\footnote{Define Finite defense-$\mbeats$-$\wibeatse$-startdec as: $\mbeatsinv(\ar) \subseteq \wibeatse(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \wibeatse(\args)$. Finite defense-$\mbeats$-$\wibeatse$-startdec is insufficient to provide $T_\eta = \iposs$. Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1, \ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar_5 \mbeats^\text{fail} \ar_4 \mbeats^\text{fail} \ar_1$. Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\wibeatse$-startdec is satisfied as there is no cover of the $\mbeats$ attacks to $\ar_1$.}
\footnote{Define Finite defense-$\mbeats$-$\mbeats$-startdec as: $\mbeatsinv(\ar) \subseteq \mbeats(\argsdec) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args)$. Finite defense-$\mbeats$-$\mbeats$-startdec is insufficient to provide $T_\eta = \iposs$. Consider $\ar_3 \wibeatse \ar_2 \wibeatse \ar_1$, $\ar_3' \wibeatse \ar_2' \wibeatse \ar_1$, and so on, and $\ar \mbeats^\text{fail} \{\ar_2, \ar_2', …\}$. Then I really need infinitely many arguments to defend $\ar_1$ but Finite defense-$\mbeats$-$\mbeats$-startdec is artificially satisfied because of $\ar$. Define Finite defense-$\mbeats$-$\mbeats$-subsets as: $\mbeatsinv(\ar) \subseteq \mbeats(\args) ⇒ \mbeatsinv(\ar) \subseteq \mbeats(\args')$ (for any $\args \subseteq \argsdec$). Finite defense-$\mbeats$-$\mbeats$-subsets is (rightly) non satisfied in this example.}
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
